% /qompassai/latex/cv/cover_letter.tex
% Qompass AI Cover Letter Template
% Copyright (C) 2025 Qompass AI, All rights reserved
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%!TEX TS-program = xelatex
%!TEX encoding = UTF-8 Unicode
%
% Author: Matt A. Porter <map@qompass.ai>
% ----------------------------------------
%

\documentclass[11pt,a4paper]{awesome-cv}
\input{vars.tex}
%-----------------------------------------------------------------------------
\usepackage{fontawesome5}
\usepackage[hidelinks]{hyperref}
\usepackage{ragged2e}
\usepackage{fontspec}
\emergencystretch=2em

\setmainfont{Lato}
\setsansfont{Lato}
\renewcommand{\familydefault}{\sfdefault}

\geometry{left=2.5cm,right=2.5cm,top=1.5cm,bottom=2cm,footskip=.5cm}
\definecolor{awesome}{HTML}{BB2528}
\colorlet{awesome}{awesome-red}
\setbool{acvSectionColorHighlight}{true}
\renewcommand{\acvHeaderSocialSep}{\quad\textbar\quad}

\providecommand{\namefont}{\fontfamily{phv}\selectfont\fontsize{24pt}{28pt}\bfseries}
\newcommand*\CustomHeader{%
  \begin{center}
  {\namefont Matt A.~Porter\\[3pt]}
  {\small Technologist {\Large\textperiodcentered} Service‑Disabled Veteran}\\[3pt]
  811 E Queen Ave, Spokane, WA 99207 \quad|\quad (+1) 509‑919‑5237\\[3pt]
  \href{mailto:map@qompass.ai}{\faEnvelope\enskip map@qompass.ai}\enskip
  \href{https://github.com/phaedrusflow}{\faGithub\enskip phaedrusflow}\enskip
  \href{https://www.linkedin.com/in/matt-a-porter-103535224}{\faLinkedin\enskip matt‑a‑porter}\enskip
  \href{https://orcid.org/0000-0002-0302-4812}{\faOrcid\enskip ORCID}\enskip
  \href{https://www.youtube.com/@qompassai}{\faIcon{youtube}\enskip Qompass AI}
\end{center}
\vspace{1.2em}
}
\recipient{\RecipientName}{\CompanyName\\\CompanyAddress}
\letterdate{\LetterDate}
\lettertitle{Application for \JobTitle}
\letteropening{Dear \RecipientName,}
\let\makeletterclosing\relax
\letterenclosure[Attached]{Resume}
\begin{document}
\setlength{\parskip}{0.8em}
\setlength{\parindent}{0pt}
\linespread{1.15}
\justifying
\CustomHeader
\makecvfooter{}{%
	\textsc{map@qompass.ai · (+1) 509‑919‑5237 · github.com/phaedrusflow}}{}

\makelettertitle
\begin{cvletter}
	\RaggedRight

	It is a pleasure to apply for the \textbf{\JobTitle} position with \CompanyName. My career has centered on expanding healthcare access through service coordination, outreach, and data‑driven innovation. I believe this role directly aligns with both my professional experience and lifelong commitment to improving equitable healthcare across Washington.

	My multidisciplinary background integrates medical, technological, and organizational leadership. As the founder of Qompass AI, I lead initiatives that combine health education and analytics to empower quality AI adoption at the intersection of healthcare and education. At Washington State University’s Elson S. Floyd College of Medicine, I co-founded a mentorship and outreach network that supported over 8,000 youth and community members, and built an AI‑enabled, knowledge‑management platform adopted college‑wide.

	Previously, as an Army Intelligence Officer, I learned to manage data integrity, coordinate with multi‑agency teams, and handle confidential information with professionalism and precision — skills directly applicable to client tracking, billing, and HIPAA‑compliant correspondence required for this role.

	I bring a practical understanding of how medical, civic, and technological systems interface. Through work with underserved clinics such as Spanaway Community Healthcare and Tacoma Neighborhood Free Clinic. I helped patients navigate referrals, insurance application, and transportation barriers — mirroring the task scope of this position.

	My certifications in HIPAA compliance, emergency medical services, and data management complement your program’s focus on accuracy and efficiency. I am also well‑versed in leveraging secure software systems for case processing, reporting, and patient outreach.

	The mission of \CompanyName{} — \emph{\CompanyMission{}} — resonates deeply with my professional and personal values. Your emphasis on proactive plan monitoring, relationship‑building, and compassionate communication reflects how I approach my work. I am eager to join an organization that shares my dedication to ensuring every patient receives the coordination, advocacy, and respect they deserve.

\vspace{1.5em}
\noindent
Respectfully,\\[1em]
Matthew A. Porter

\end{cvletter}
\end{document}
